Exploring Hillary Clinton's Emails\thanks{STATS 601 final project. All of the code used to download, process, and analyze the data for this project is available at \url{https://github.com/lbybee/601_Final_Project} and has been open-sourced under the MIT license.}

### 2016-04-21 paper/paper.tex
some editing

\section{Introduction}
From roughly 2008 to 2013, Hillary Clinton and some of her staff used a private family email server for most of he communication. This time period includes her tenure as U.S. Secretary of State, and has therefore become a controversial topic due to the possible security concerns of not using official government servers. Various investigations into the legality and appropriateness of the email server have been launched, and the issue has had/will potentiall have a large effect on Clinton's ongoing presidential campaign.

Due to several Freedom of Information Act (FOIA), the State Department has released the vast majority of the roughly 55,000 pages of emails to the public, leading to an unprecedented opportunity to explore the email usage of a major public figure.

@@

\subsection{Topic Analysis}
We can also look into specific topics in more detail to see what they consist of and how they might correspond to real-world events. Table~\ref{tab:content_topics} shows the top 10 words for six topics that are all examples of content topics. In particular, these topics correspond to specific politically significant events or issues. For instance, the Libya topic seems to capture discussion about the Benghazi scandal as well the collapse of Gaddafi's administration.

@@

\begin{table}[htb] \centering \scriptsize
\begin{tabular}{cccccc}
  \toprule
  Israel & Elections & Libya & Afghanistan & Int. Dev. & Obama \\
  \midrule
  Sidney Blumenthal & SB & Huma Abedin & Judith McHale & JM & SB \\
  (SB) & & (HA) & (JM) & & \\
  \noalign{\vskip 5mm}
  HA & Philippe Reines & Wendy Sherman & HA & Melanne Verveer & PR \\
  & (PR) & (WS) & & (MV) & \\
  \noalign{\vskip 5mm}
  Jake Sullivan & JM & JS & MV & Anne-Marie & Cherly Mills \\
  (JS) & & & & Slaughter (AMS) & (CM)\\
  \noalign{\vskip 5mm}
  AMS & CM & Monica Hanley & JS & CM & HA \\
  & & (MH) & & & \\
  \noalign{\vskip 5mm}
  Hillary Clinton & HA & SB & Richard Verma & JS & HC \\
  (HC) & & & (RV) & & \\
  \bottomrule
\end{tabular}
\caption{Primary senders for some example topics}
\label{tab:top_senders}
\end{table}

>>>>

\section{Introduction}
From roughly 2008 to 2013, Hillary Clinton and some of her staff used a private family email server for most of their communication. This time period includes her tenure as U.S. Secretary of State, and has therefore become a controversial topic due to the possible security concerns of not using official government servers. Various investigations into the legality and appropriateness of the email server have been launched, and the issue has had and will potentially have a significant effect on Clinton's ongoing presidential campaign.

Due to the Freedom of Information Act (FOIA), the State Department has released the vast majority of the roughly 55,000 pages of emails to the public, leading to an unprecedented opportunity to explore the email usage of a major public figure.

@@

\subsection{Topic Analysis}
We can also look into specific topics in more detail to see what they consist of and how they might correspond to real-world events. Table~\ref{tab:content_topics} shows the top 10 words for six topics that are all examples of content topics. In particular, these topics correspond to specific politically significant events or issues. For instance, the Libya topic seems to capture discussion about the Benghazi scandal as well the collapse of Muammar Gaddafi's administration.

@@

\begin{table}[htb] \centering \scriptsize
\begin{tabular}{cccccc}
  \toprule
  Topic 6     & Topic 11   & Topic 18 & Topic 27    & Topic 23  & Topic 25 \\
  Israel      & Elections  & Libya    & Afghanistan & Int. Dev. & Obama \\
  \midrule
  Sidney Blumenthal & SB & Huma Abedin & Judith McHale & JM & SB \\
  (SB) & & (HA) & (JM) & & \\
  \noalign{\vskip 5mm}
  HA & Philippe Reines & Wendy Sherman & HA & Melanne Verveer & PR \\
  & (PR) & (WS) & & (MV) & \\
  \noalign{\vskip 5mm}
  Jake Sullivan & JM & JS & MV & Anne-Marie & Cherly Mills \\
  (JS) & & & & Slaughter (AMS) & (CM)\\
  \noalign{\vskip 5mm}
  AMS & CM & Monica Hanley & JS & CM & HA \\
  & & (MH) & & & \\
  \noalign{\vskip 5mm}
  Hillary Clinton & HA & SB & Richard Verma & JS & HC \\
  (HC) & & & (RV) & & \\
  \bottomrule
\end{tabular}
\caption{Primary senders for some example topics}
\label{tab:top_senders}
\end{table}
